\begin{center}
  \section*{Abstract}
\end{center}

\addcontentsline{toc}{section}{Abstract}

\begin{spacing}{1.5}
The expansion of Internet of Things (IoT) infrastructure in Saudi Arabia under Vision 2030 will lead to the development of smart cities.
The increasing number of unsecured devices throughout systems has created an environment which makes botnet attacks more dangerous. This
The TrapPot system operates as a unified platform which performs observation tasks through its Artificial Intelligence (AI) system.
analyze, and automatically classify malicious activities targeting IoT environments to enhance
proactive security readiness The research uses quantitative case study methodology to analyze the data.
lizing a medium-interaction Cowrie honeypot to emulate Telnet and Secure Shell (SSH) services
within a strictly isolated network . The ELK Stack analyzes data from actual attack logs which serve as its input.
(Elasticsearch, Logstash, and Kibana) for real-time monitoring, while a data pipeline extracts
behavioral features, such as login attempts and session duration, to train a Random Forest (RF)
classification model The design phase has produced a comprehensive system architecture and
feature engineering strategy focused on identifying four distinct attack types: brute-force, scan-
ning, malware download, and command execution . The research design uses a particular method which serves to achieve its research objectives.
target classification accuracy of 96TrapPot distinguishes itself by combining automated machine
The system enables students to learn through real-time visualization tools which fulfill specific cybersecurity workforce needs that exist in various geographic locations.
development needs in Saudi Arabia . The project reached its goal which allowed us to accomplish all our practice objectives.
tical framework for transitioning from reactive to proactive defense strategies within the rapidly
evolving IoT threat landscape.\\

  {\bf Keywords:} TrapPot, Internet of Things (IoT), Honeypot, Random Forest (RF), Cybersecurity, Artificial Intelligence (AI).
\end{spacing}
\clearpage
